Towards Spherical Robots for Mobile Mapping in Human Made Environments\tnoteref{mytitlenote}

### 2021-07-12 Latex/sections/simulation.tex
images moved

Figure~\ref{fig:simulatedDatasets} shows a noise-free trajectory through a simulated environment and a trajectory with noisy sensors while figure~\ref{fig:robotRender} shows a rendering of the simulated robot as well as the simulation sequence. 
In the noise-free case, the trajectory slightly bends in the direction of disturbance torque sideways while also varying in velocity in the intended direction of travel.
In the noisy case, the ideal straight trajectory is assumed.
Hence the planes enclosing the room are sensed multiple times. 
In particular, we see that the trajectory of the robot leads through one of the sensed planes. 
Also, the further the sensed points are, the noisier they appear, which is consistent with the larger influence of the pose error at higher distances.

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.495\textwidth]{images/sim_frame_00.png}\hfill
	\includegraphics[width=0.495\textwidth]{images/sim_frame_02.png}\\
	\includegraphics[width=0.495\textwidth]{images/sim_frame_06.png}\hfill
	\includegraphics[width=0.495\textwidth]{images/sim_frame_08.png}\\
	\includegraphics[width=0.495\textwidth]{images/ProtoRoll1.png}\hfill
	\includegraphics[width=0.495\textwidth]{images/ProtoRoll2.png}
	\caption{Top: Initial sequence of the simulation of the ideal dataset showing the simulated motion of the robot.
	Below: Rendering of the simulated robot, a Livox laser scanner insider a spherical shell.}
	\label{fig:robotRender}
\end{figure*}

>>>>

Figure~\ref{fig:simulatedDatasets} shows a noise-free trajectory through a simulated environment and a trajectory with noisy sensors while figure~\ref{fig:robotRender} shows a rendering of the simulation sequence.
In the noise-free case, the trajectory slightly bends in the direction of disturbance torque sideways while also varying in velocity in the intended direction of travel.
In the noisy case, the ideal straight trajectory is assumed.
Hence the planes enclosing the room are sensed multiple times. 
In particular, we see that the trajectory of the robot leads through one of the sensed planes. 
Also, the further the sensed points are, the noisier they appear, which is consistent with the larger influence of the pose error at higher distances.

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.495\textwidth]{images/sim_frame_00.png}\hfill
	\includegraphics[width=0.495\textwidth]{images/sim_frame_02.png}\\
	\includegraphics[width=0.495\textwidth]{images/sim_frame_06.png}\hfill
	\includegraphics[width=0.495\textwidth]{images/sim_frame_08.png}\\
	\caption{Top: Initial sequence of the simulation of the ideal dataset showing the simulated motion of the robot.
	\label{fig:robotRender}
\end{figure*}
